---
title: "PreregistrationEvaluation_Main_Raw_Processed"
author: "Marton Kovacs & Bence Bakos"
date: "18/12/2020"
output: html_document
---

# Load packages

```{r packages}
library(tidyverse)
```

# Import data

```{r import data}
raw_data <- read_tsv("Data/Main/Raw/PreregistrationEvaluation_Main_Raw.tsv")
raw_data <- janitor::clean_names(raw_data)
```

# Changing response

R_Z3mrRm2XJpVRZcd  meant to respond strongly agree: 'For the question about whether preregistration made it easier to avoid questionable research practices, I meant to select "Strongly agree", but selected "strongly disagree" by mistake. Please change my response to "Strongly Agree"'

The respondent actually gave the "Very Strongly Disagree" answer.

```{r changing response}
raw_data <- raw_data %>%
  mutate(other_qrp = case_when(response_id == "R_Z3mrRm2XJpVRZcd" ~ "Strongly Agree",
                                                     TRUE ~ other_qrp))
```


# Filtering responses

The analysis will concentrate only on the answers of the Preregistration Group and the Control Group. Unfinished responses are excluded. Participants who did not accept the informed consent form are excluded. An attention check was also included.

```{r}
#removing Qualtrics labels
label <-
  raw_data %>% 
  slice(1:2)

raw_data <-
  raw_data %>% 
  slice(-(1:2))


group_interest <- c("prereg", "control")

filtered_data <- raw_data %>% 
  filter(finished == "True",
         progress == "100",
         informed_consent == "Yes",
         group %in% group_interest,
         group == "control" & control_attention == "4\nFour" | 
           group == "prereg" & prereg_attention == "4\nFour")

#How many respondents do we have from the Prereg and the Control groups?
filtered_data %>% 
  count(group)

#How many respondents do we have from each research type?
filtered_data %>% 
  count(research_type)
```

# Removing irrelevant variables

```{r removing}
filtered_data <- filtered_data %>% 
  select(response_id, control_hypothesis:prereg_qrp, planning:changed_comment) %>% 
  select(-c(control_attention, prereg_attention))

glimpse(filtered_data)
```

# Tidying and recoding data

Several response variables need to be recoded to numeric values. As a first step, several keys are created to make the recoding process easier. Second, the keys are applied.

```{r tidying}
tidy_data <- 
  filtered_data %>% 
  # Gather all the columns with "prereg_" or "control_" prefix
  pivot_longer(
    cols = union(contains("prereg_"),contains("control_")),
    names_to = "variable_names",
    values_to = "values"
  ) %>% 
  # Response was forced so all NA values mean that the participant was not member of that group
  # So we can drop them
  drop_na(values) %>% 
  # Delete prefix and convert character variables to numeric
  mutate(variable_names = str_remove(variable_names, "prereg_|control_"),
         # Because there is a mismatch in the variable names between the control and prereg group
         variable_names = case_when(variable_names == "rmd" ~ "rdm",
                                    TRUE ~ variable_names),
         values = case_when(values == "I do not know" ~ "0",
                            values == "Not applicable" ~ "99",
                            values == "Very Strongly Disagree" ~ "1",
                            values == "Strongly Disagree" ~ "2",
                            values == "Disagree" ~ "3",
                            values == "Neither Agree or Disagree" ~ "4",
                            values == "Agree" ~ "5",
                            values == "Strongly Agree" ~ "6",
                            values == "Very Strongly Agree" ~ "7",
                            TRUE ~ values),
         values = as.integer(str_extract(values, "[0-9]{1,2}"))) %>% 
  # Spread gathered columns to make the datatable tidy
  pivot_wider(
    names_from = variable_names,
    values_from = values
  )
```


# Write data

```{r export}
write_tsv(tidy_data, "Data/Main/Processed/Import/PreregistrationEvaluation_Main_Processed.tsv")
```